---
title: Template for RFMO working papers
author:
  - name: Alice Anonymous
    email: alice@example.com
    corresponding_author: TRUE # Automatic author note including email address
    affiliation:
      - ABC
      - DEF
  - name: Bob Security
    email: bob@example.com
    affiliation: DEF
    footnote: 1 # Author note using reference
  - name: Cat Memes
    email: cat@anotheru.edu
    affiliation: Another University
    footnote:
        - 1
        - 2
address:
  - code: ABC
    address: University of Somewhere
  - code: DEF
    address: Address in one element deprecated, but works
  - code: Another University
    address: Address for Another University
footnote:
  - code: 1
    text: "Equal contribution"
  - code: 2
    text: "Current email address: [cat@example.com](mailto:cat@example.com)"
#classoptions:
#  - a4paper # Can also be here
bibliography: mybibfile.bib
csl: dmk-format.csl # Use any CSL style. Ignored if citation_package: natbib
link-citations: TRUE
output:
  pdf_document:
    keep_tex: TRUE
    template: generic_template.tex
    md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: TRUE
# endfloatoption:
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: FALSE # Set to false to put author affiliations in footnotes
footnotehyper: FALSE # Needed to be able to use French blocks
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE
tables: TRUE
fancyhdr:
  first:
    headleft: "Report No. 1"
    headright: "Kaplan et al. (2021)"
    headrulewidth: 0pt
    #footleft: A left foot
    footrulewidth: 0pt
  subsequent:
    headright: "*Kaplan et al. (2021)*" # Italics
    headrulewidth: 1pt
    footrulewidth: 0pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # By default, hide code; set to TRUE to see code
knitr::opts_chunk$set(fig.pos = 'th') # Places figures at top or here
knitr::opts_chunk$set(out.width = '100%', dpi=300) # Figure resolution and size
knitr::opts_chunk$set(fig.env="figure") # Latex figure environment

options(knitr.table.format="latex") # For kable tables to work without setting format option

# If package not installed, install it
if (!requireNamespace("knitrdata")) {
  if (!requireNamespace("remotes"))
    install.packages("remotes")
  remotes::install_github("dmkaplan2000/knitrdata",build_vignettes = TRUE)  
}

library(knitrdata) # load package
```

::: {.abstract data-latex="" lang=en}
An abstract text.

Second paragraph.
:::

::: {.keywords data-latex="" lang=en}
Keyword1; Keyword2
:::

<!-- Define as portuguese as spanish causes weird failure -->
<!-- Use class renameableabstract to give abstract a different title -->
::: {.renameableabstract data-latex="[Resumen]" lang=pt}
Un poco de texto.
:::

::: {.keywords data-latex="[Palabras Claves]" lang=pt}
Palabra1; Palabra2
:::

::: {.abstract data-latex="" lang=fr}
Un peu de texte.
:::

::: {.keywords data-latex="[Mots clés]" lang=fr}
Mot1; Mot2
:::

# Introduction

This template is a generic paper template that can be used for lots of tasks, including creating working group papers and as a starter format for publications for which one has not yet decided on a final format.

## A subsection

A numbered list:

1) First point
2) Second point
    - Subpoint
    
A bullet list:

* First point
* Second point

# Literature citations

By default, citations are handled using CSQL style files, but `natbib` citations are also possible.

Here are two sample references: 

* **author (year) example:** @horvath2018dna showed some really cool things.
* **(author year) example:** This is a well known result [@ji20123d]. 

The bibliography will appear at the end of the document.

# Equations

An equation without a label for cross-referencing:

$$
E=mc^2
$$

An inline equation: $y=ax+b$

An equation with a label for cross-referencing:

\begin{equation}\label{eq:eq1}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = 1
\end{equation}

This equation can be referenced as follows: Eq. \ref{eq:eq1}

# Inserting R figures

The code below creates a figure. The code is included in the output because `echo=TRUE`.

```{r fig1, fig.cap="This is the first figure.",echo=TRUE}
plot(1:10,main="Some data",xlab="Distance (cm)",
     ylab="Time (hours)")
```

You can reference this figure as follows: Fig. \ref{fig:fig1}.

# Tables

## Generate a table using `xtable`

```{r xtabletable, results="asis", echo=TRUE}
df = data.frame(ID=1:3,code=letters[1:3])

# Creates tables that follow OUP guidelines 
# using xtable
library(xtable) 
print(xtable(df,caption="This is a xtable table.",
             label="tab:tab1"),
      comment=FALSE,caption.placement="top")
```

You can reference this table as follows: Table \ref{tab:tab1}.

## Generate a table using `kable`

```{r kabletable, echo=TRUE}
df = data.frame(ID=1:3,code=letters[1:3])

# kable can alse be used for creating tables
knitr::kable(df,caption="This is a kable table.",
             #format="latex",
             booktabs=TRUE,label="tab2")
```

You can reference this table as follows: Table \ref{tab:tab2}.


# Cross-referencing sections

You can cross-reference sections and subsections as follows: Section \ref{literature-citations} and Section \ref{a-subsection}.

For more portable and flexible referencing of sections, equations, figures and tables, use [`bookdown::pdf_document2`](https://github.com/rstudio/bookdown).

***Note:*** the last section in the document will be used as the section title for the bibliography.

<!-- An unnumbered section with the acknowledgements-->
# Acknowledgements {-}

This is an acknowledgement.

It consists of two paragraphs.

# References

<!-- Don't edit after this point. Creates latex template for document. -->
```{data generictemplatetex, format = "text", encoding = "asis", output.file = "generic_template.tex", echo = FALSE, eval=!file.exists("generic_template.tex"),line.sep="\n"}
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode$for(hyperrefoptions)$,$hyperrefoptions$$endfor$}{hyperref}
\PassOptionsToPackage{hyphens}{url}
$if(colorlinks)$
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
$endif$
$if(dir)$
$if(latex-dir-rtl)$
\PassOptionsToPackage{RTLdocument}{bidi}
$endif$
$endif$
$if(CJKmainfont)$
\PassOptionsToPackage{space}{xeCJK}
$endif$
%
\documentclass[
$if(fontsize)$
  $fontsize$,
$endif$
$if(lang)$
  $babel-lang$,
$endif$
$if(papersize)$
  $papersize$paper,
$endif$
$if(beamer)$
  ignorenonframetext,
$if(handout)$
  handout,
$endif$
$if(aspectratio)$
  aspectratio=$aspectratio$,
$endif$
$endif$
$for(classoption)$
  $classoption$$sep$,
$endfor$
]{$documentclass$}
$if(beamer)$
$if(background-image)$
\usebackgroundtemplate{%
  \includegraphics[width=\paperwidth]{$background-image$}%
}
$endif$
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbols$if(navigation)$$navigation$$else$empty$endif$
$for(beameroption)$
\setbeameroption{$beameroption$}
$endfor$
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
$if(section-titles)$
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
$endif$
$endif$
$if(beamerarticle)$
\usepackage{beamerarticle} % needs to be loaded first
$endif$
\usepackage{amsmath,amssymb}
$if(fontfamily)$
\usepackage[$for(fontfamilyoptions)$$fontfamilyoptions$$sep$,$endfor$]{$fontfamily$}
$else$
\usepackage{lmodern}
$endif$
$if(linestretch)$
\usepackage{setspace}
$endif$
\usepackage{iftex}
\ifPDFTeX
  \usepackage[$if(fontenc)$$fontenc$$else$T1$endif$]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
$if(mathspec)$
  \ifXeTeX
    \usepackage{mathspec}
  \else
    \usepackage{unicode-math}
  \fi
$else$
  \usepackage{unicode-math}
$endif$
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
$if(mainfont)$
  \setmainfont[$for(mainfontoptions)$$mainfontoptions$$sep$,$endfor$]{$mainfont$}
$endif$
$if(sansfont)$
  \setsansfont[$for(sansfontoptions)$$sansfontoptions$$sep$,$endfor$]{$sansfont$}
$endif$
$if(monofont)$
  \setmonofont[$for(monofontoptions)$$monofontoptions$$sep$,$endfor$]{$monofont$}
$endif$
$for(fontfamilies)$
  \newfontfamily{$fontfamilies.name$}[$for(fontfamilies.options)$$fontfamilies.options$$sep$,$endfor$]{$fontfamilies.font$}
$endfor$
$if(mathfont)$
$if(mathspec)$
  \ifXeTeX
    \setmathfont(Digits,Latin,Greek)[$for(mathfontoptions)$$mathfontoptions$$sep$,$endfor$]{$mathfont$}
  \else
    \setmathfont[$for(mathfontoptions)$$mathfontoptions$$sep$,$endfor$]{$mathfont$}
  \fi
$else$
  \setmathfont[$for(mathfontoptions)$$mathfontoptions$$sep$,$endfor$]{$mathfont$}
$endif$
$endif$
$if(CJKmainfont)$
  \ifXeTeX
    \usepackage{xeCJK}
    \setCJKmainfont[$for(CJKoptions)$$CJKoptions$$sep$,$endfor$]{$CJKmainfont$}
  \fi
$endif$
$if(luatexjapresetoptions)$
  \ifLuaTeX
    \usepackage[$for(luatexjapresetoptions)$$luatexjapresetoptions$$sep$,$endfor$]{luatexja-preset}
  \fi
$endif$
$if(CJKmainfont)$
  \ifLuaTeX
    \usepackage[$for(luatexjafontspecoptions)$$luatexjafontspecoptions$$sep$,$endfor$]{luatexja-fontspec}
    \setmainjfont[$for(CJKoptions)$$CJKoptions$$sep$,$endfor$]{$CJKmainfont$}
  \fi
$endif$
\fi
$if(zero-width-non-joiner)$
%% Support for zero-width non-joiner characters.
\makeatletter
\def\zerowidthnonjoiner{%
  % Prevent ligatures and adjust kerning, but still support hyphenating.
  \texorpdfstring{%
    \textormath{\nobreak\discretionary{-}{}{\kern.03em}%
      \ifvmode\else\nobreak\hskip\z@skip\fi}{}%
  }{}%
}
\makeatother
\ifPDFTeX
  \DeclareUnicodeCharacter{200C}{\zerowidthnonjoiner}
\else
  \catcode`^^^^200c=\active
  \protected\def ^^^^200c{\zerowidthnonjoiner}
\fi
%% End of ZWNJ support
$endif$
$if(beamer)$
$if(theme)$
\usetheme[$for(themeoptions)$$themeoptions$$sep$,$endfor$]{$theme$}
$endif$
$if(colortheme)$
\usecolortheme{$colortheme$}
$endif$
$if(fonttheme)$
\usefonttheme{$fonttheme$}
$endif$
$if(mainfont)$
\usefonttheme{serif} % use mainfont rather than sansfont for slide text
$endif$
$if(innertheme)$
\useinnertheme{$innertheme$}
$endif$
$if(outertheme)$
\useoutertheme{$outertheme$}
$endif$
$endif$
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[$for(microtypeoptions)$$microtypeoptions$$sep$,$endfor$]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
$if(indent)$
$else$
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
$endif$
$if(verbatim-in-note)$
\usepackage{fancyvrb}
$endif$
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
$if(title-meta)$
  pdftitle={$title-meta$},
$endif$
$if(author-meta)$
  pdfauthor={$author-meta$},
$endif$
$if(lang)$
  pdflang={$lang$},
$endif$
$if(subject)$
  pdfsubject={$subject$},
$endif$
$if(keywords)$
  pdfkeywords={$for(keywords)$$keywords$$sep$, $endfor$},
$endif$
$if(colorlinks)$
  colorlinks=true,
  linkcolor={$if(linkcolor)$$linkcolor$$else$Maroon$endif$},
  filecolor={$if(filecolor)$$filecolor$$else$Maroon$endif$},
  citecolor={$if(citecolor)$$citecolor$$else$Blue$endif$},
  urlcolor={$if(urlcolor)$$urlcolor$$else$Blue$endif$},
$else$
  hidelinks,
$endif$
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
$if(verbatim-in-note)$
\VerbatimFootnotes % allow verbatim text in footnotes
$endif$
$if(geometry)$
$if(beamer)$
\geometry{$for(geometry)$$geometry$$sep$,$endfor$}
$else$
\usepackage[$for(geometry)$$geometry$$sep$,$endfor$]{geometry}
$endif$
$endif$
$if(beamer)$
\newif\ifbibliography
$endif$
$if(listings)$
\usepackage{listings}
\newcommand{\passthrough}[1]{#1}
\lstset{defaultdialect=[5.3]Lua}
\lstset{defaultdialect=[x86masm]Assembler}
$endif$
$if(lhs)$
\lstnewenvironment{code}{\lstset{language=Haskell,basicstyle=\small\ttfamily}}{}
$endif$
$if(highlighting-macros)$
$highlighting-macros$
$endif$
$if(tables)$
\usepackage{longtable,booktabs,array}
$if(multirow)$
\usepackage{multirow}
$endif$
\usepackage{calc} % for calculating minipage widths
$if(beamer)$
\usepackage{caption}
% Make caption package work with longtable
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
$else$
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
$if(footnotehyper)$
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
$else$
\usepackage{footnote} % For some unknown reason, footnotehyper clashes with French
$endif$
\makesavenoteenv{longtable}
$endif$
$endif$
$if(graphics)$
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
$endif$
$if(links-as-notes)$
% Make links footnotes instead of hotlinks:
\DeclareRobustCommand{\href}[2]{#2\footnote{\url{#1}}}
$endif$
$if(strikeout)$
$-- also used for underline
\usepackage[normalem]{ulem}
% Avoid problems with \sout in headers with hyperref
\pdfstringdefDisableCommands{\renewcommand{\sout}{}}
$endif$
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
$if(numbersections)$
\setcounter{secnumdepth}{$if(secnumdepth)$$secnumdepth$$else$5$endif$}
$else$
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
$endif$
$if(beamer)$
$else$
$if(block-headings)$
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
$endif$
$endif$
$if(pagestyle)$
\pagestyle{$pagestyle$}
$endif$
$if(csl-refs)$
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% dont indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
$endif$

%%%%%%%% START HEADER PARTIAL %%%%%%%%%%%%

% Formatting of tables & knitr::kable and kableExtra functionality
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

% Line numbering
$if(numberlines)$
\usepackage$if(numberlines-options)$[$numberlines-options[,]$]$endif${lineno}
\linenumbers
$endif$

% endfloat stuff
$if(endfloat)$
\usepackage[$if(endfloatoption)$$for(endfloatoption)$$endfloatoption$$sep$,$endfor$$else$tablesfirst,nomarkers$endif$]{endfloat}
$endif$

% fancyhdr pagestyle
$if(fancyhdr)$
\usepackage{fancyhdr}

$if(fancyhdr.first)$
\fancypagestyle{myfirst}{%
\fancyfoot[C]{\thepage}% Default to just page number
%
$if(fancyhdr.first.headleft)$
\fancyhead[L]{$fancyhdr.first.headleft$}%
$endif$
$if(fancyhdr.first.headcenter)$
\fancyhead[C]{$fancyhdr.first.headcenter$}%
$endif$
$if(fancyhdr.first.headright)$
\fancyhead[R]{$fancyhdr.first.headright$}%
$endif$
$if(fancyhdr.first.headrulewidth)$
\renewcommand{\headrulewidth}{$fancyhdr.first.headrulewidth$}
$endif$
%
$if(fancyhdr.first.footleft)$
\fancyfoot[L]{$fancyhdr.first.footleft$}%
$endif$
$if(fancyhdr.first.footcenter)$
\fancyfoot[C]{$fancyhdr.first.footcenter$}%
$endif$
$if(fancyhdr.first.footright)$
\fancyfoot[R]{$fancyhdr.first.footright$}%
$endif$
$if(fancyhdr.first.footrulewidth)$
\renewcommand{\footrulewidth}{$fancyhdr.first.footrulewidth$}
$endif$
}
$endif$

$if(fancyhdr.subsequent)$
\fancypagestyle{mysubsequent}{%
\fancyfoot[C]{\thepage}% Default to just page number
%
$if(fancyhdr.subsequent.headleft)$
\fancyhead[L]{$fancyhdr.subsequent.headleft$}%
$endif$
$if(fancyhdr.subsequent.headcenter)$
\fancyhead[C]{$fancyhdr.subsequent.headcenter$}%
$endif$
$if(fancyhdr.subsequent.headright)$
\fancyhead[R]{$fancyhdr.subsequent.headright$}%
$endif$
$if(fancyhdr.subsequent.headrulewidth)$
\renewcommand{\headrulewidth}{$fancyhdr.subsequent.headrulewidth$}
$endif$
%
$if(fancyhdr.subsequent.footleft)$
\fancyfoot[L]{$fancyhdr.subsequent.footleft$}%
$endif$
$if(fancyhdr.subsequent.footcenter)$
\fancyfoot[C]{$fancyhdr.subsequent.footcenter$}%
$endif$
$if(fancyhdr.subsequent.footright)$
\fancyfoot[R]{$fancyhdr.subsequent.footright$}%
$endif$
$if(fancyhdr.subsequent.footrulewidth)$
\renewcommand{\footrulewidth}{$fancyhdr.subsequent.footrulewidth$}
$endif$
}
$endif$

$endif$

% Environment for keywords
\makeatletter
\newcommand\keywordsname{Keywords}
\newenvironment*{keywords}[1][\keywordsname]{\if@twocolumn \else \small \quotation \fi \textbf{\textit{#1 ---}}}{\if@twocolumn \else \small \endquotation \fi}
\makeatother

% Environment for abstract that takes new abstract name
\newenvironment{renameableabstract}[1][\abstractname]{\let\oldabstractname\abstractname \renewcommand{\abstractname}{#1} \begin{abstract}}{\end{abstract} \renewcommand{\abstractname}{\oldabstractname}}

%%%%%%%% END HEADER PARTIAL %%%%%%%%%%%%

$for(header-includes)$
$header-includes$
$endfor$
$if(lang)$
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[$for(polyglossia-lang.options)$$polyglossia-lang.options$$sep$,$endfor$]{$polyglossia-lang.name$}
$for(polyglossia-otherlangs)$
  \setotherlanguage[$for(polyglossia-otherlangs.options)$$polyglossia-otherlangs.options$$sep$,$endfor$]{$polyglossia-otherlangs.name$}
$endfor$
\else
  \usepackage[$for(babel-otherlangs)$$babel-otherlangs$,$endfor$main=$babel-lang$]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
$if(babel-newcommands)$
  $babel-newcommands$
$endif$
\fi
$endif$
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
$if(dir)$
\ifXeTeX
  % Load bidi as late as possible as it modifies e.g. graphicx
  \usepackage{bidi}
\fi
\ifPDFTeX
  \TeXXeTstate=1
  \newcommand{\RL}[1]{\beginR #1\endR}
  \newcommand{\LR}[1]{\beginL #1\endL}
  \newenvironment{RTL}{\beginR}{\endR}
  \newenvironment{LTR}{\beginL}{\endL}
\fi
$endif$
$if(natbib)$
\usepackage[$natbiboptions$]{natbib}
\bibliographystyle{$if(biblio-style)$$biblio-style$$else$plainnat$endif$}
$endif$
$if(biblatex)$
\usepackage[$if(biblio-style)$style=$biblio-style$,$endif$$for(biblatexoptions)$$biblatexoptions$$sep$,$endfor$]{biblatex}
$for(bibliography)$
\addbibresource{$bibliography$}
$endfor$
$endif$
$if(nocite-ids)$
\nocite{$for(nocite-ids)$$it$$sep$, $endfor$}
$endif$
$if(csquotes)$
\usepackage{csquotes}
$endif$

$if(title)$
\title{$title$$if(thanks)$\thanks{$thanks$}$endif$}
$endif$
$if(subtitle)$
$if(beamer)$
$else$
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
$endif$
\subtitle{$subtitle$}
$endif$

%%%%%%% START AUTHOR PARTIAL %%%%%%%%%%%%%%%

%%%%% Authors, affiliations and author notes stuff %%%%%

% Macros for creating and referencing stored reference
\makeatletter
\def\MyNewLabel#1#2#3{\expandafter\gdef\csname #1@#2\endcsname{#3}}

\def\MyRef#1#2{\@ifundefined{#1@#2}{???}{\csname #1@#2\endcsname}}

\newcommand*\ifcounter[1]{%
  \ifcsname c@#1\endcsname
    \expandafter\@firstoftwo
  \else
    \expandafter\@secondoftwo
  \fi
}
\makeatother

% Create labels for Addresses if the are given by code
$for(address)$
\MyNewLabel{ADDRTXT}{$address.code$}{$address.address$}
$endfor$

% Create labels for Footnotes if they are given by code
$for(footnote)$
\MyNewLabel{ANOTETXT}{$footnote.code$}{$footnote.text$}
$endfor$

%%% Special footnotes for addresses and author footnotes
\usepackage{bigfoot}
\DeclareNewFootnote{Addr}[arabic] % Only used for NOT authblk
\DeclareNewFootnote{ANote}[fnsymbol]

%%% Address and author notes as a function of format %%%
$if(authblk)$ % Use authblk for affiliations %%%%%%%%%%%
\usepackage{authblk}

% Always separate by commas
\renewcommand\Authsep{, }
\renewcommand\Authand{, }
\renewcommand\Authands{, }

% Counter for addresses and footnotes
\newcounter{addrcnt}

% thanks definition that doesnt produce superscript marks
\makeatletter
\newcommand*\createaddrlblbycode[1]{%
  \ifcounter{ADDRLBL@#1}
    {}
    {\refstepcounter{addrcnt}\newcounter{ADDRLBL@#1}\setcounter{ADDRLBL@#1}{\value{addrcnt}}}%
}

\newcommand*\addrlblbycode[1]{\arabic{ADDRLBL@#1}}

\newcommand*\addrbycode[1]{%
  \ifcounter{ADDR@#1}
    {}
    {\newcounter{ADDR@#1}%
     \affil[\addrlblbycode{#1}]{\MyRef{ADDRTXT}{#1}}}%
}

\newcommand*\createanotelblbycode[1]{%
  \ifcounter{ANOTELBL@#1}
    {}
    {\refstepcounter{footnoteANote}\newcounter{ANOTELBL@#1}\setcounter{ANOTELBL@#1}{\value{footnoteANote}}}%
}

\newcommand*\anotelblbycode[1]{\fnsymbol{ANOTELBL@#1}}

\newcommand*\anotebycode[1]{%
  \ifcounter{ANOTE@#1}
    {}
    {\newcounter{ANOTE@#1}%
     \footnotetextANote[\value{ANOTELBL@#1}]{\MyRef{ANOTETXT}{#1}}}%
}
\makeatother

$for(author)$

$for(author.affiliation)$
\createaddrlblbycode{$author.affiliation$}
$endfor$

$if(author.corresponding_author)$
\MyNewLabel{ANOTETXT}{$author.name$@CORRESP}{Corresponding author. \href{mailto:$author.email$}{\nolinkurl{$author.email$}}}
\makeatletter\createanotelblbycode{$author.name$@CORRESP}\makeatother
$endif$

$for(author.footnote)$
\createanotelblbycode{$author.footnote$}
$endfor$

\author[%
$for(author.affiliation)$
\addrlblbycode{$author.affiliation$}%
$sep$,%
$endfor$
$if(author.corresponding_author)$
$if(author.affiliation)$,$endif$%
\makeatletter\anotelblbycode{$author.name$@CORRESP}\makeatother
$endif$
$if(author.footnote)$
$if(author.corresponding_author)$,$elseif(author.affiliation)$,$endif$%
$for(author.footnote)$
$$\anotelblbycode{$author.footnote$}$$%
$sep$,%
$endfor$
$endif$
]{$author.name$}

$for(author.affiliation)$
\addrbycode{$author.affiliation$}
$endfor$

$endfor$

$else$ % Use footnotes for affiliations %%%%%%%%%%%%%

% Get rid of redefinition of \@makefnmark in \maketitle
% Gets rid of spacing issues
\usepackage{etoolbox}
\makeatletter
\patchcmd\maketitle{\def\@makefnmark{\rlap{\@textsuperscript{\normalfont\@thefnmark}}}}{}{}{}
\makeatother

% Hook into the \@thanks command
\makeatletter
\def\thanksAddr#1{% <--- These %'s are necessary for spacing
  \footnotemarkAddr\protected@xdef\@thanks{\@thanks%
        \protect\footnotetextAddr[\the \c@footnoteAddr]{#1}}%
}
\def\thanksANote#1{%
  \footnotemarkANote%
  \protected@xdef\@thanks{\@thanks%
        \protect\footnotetextANote[\the \c@footnoteANote]{#1}}%
}

\newcommand*\thanksAddrbycode[1]{%
  \ifcounter{ADDR@#1}
    {\footnotemarkAddr[\value{ADDR@#1}]}
    {\newcounter{ADDR@#1}%
     \thanksAddr{\MyRef{ADDRTXT}{#1}}%
     \setcounter{ADDR@#1}{\value{footnoteAddr}}} % Note sure this will work
}

\newcommand*\thanksANotebycode[1]{%
  \ifcounter{ANOTE@#1}
    {\footnotemarkANote[\value{ANOTE@#1}]}
    {\newcounter{ANOTE@#1}%
     \thanksANote{\MyRef{ANOTETXT}{#1}}%
     \setcounter{ANOTE@#1}{\value{footnoteANote}}} % Note sure this will work
}
\makeatother

\newcommand*\authsep{, }
\newcommand*\thankssep{$$^{,}$$}

$if(author)$
\author{%
$for(author)$
$author.name$%
$for(author.affiliation)$
\thanksAddrbycode{$author.affiliation$}%
$sep$\thankssep%
$endfor$
$if(author.corresponding_author)$
$if(author.affiliation)$\thankssep$endif$% extra comma
\thanksANote{Corresponding author. \href{mailto:$author.email$}{\nolinkurl{$author.email$}}} % space here seems necessary to get spacing right
$endif$
$if(author.footnote)$$if(author.affiliation)$\thankssep$elseif(author.corresponding_author)$\thankssep$endif$$endif$% extra comma
$for(author.footnote)$
\thanksANotebycode{$author.footnote$}%
$sep$\thankssep%
$endfor$
$sep$\authsep%
$endfor$
}
$endif$%endif(author)
$endif$%endif(authblk)

%%%%%%%%% END AUTHOR PARTIAL %%%%%%%%

\date{$date$}
$if(beamer)$
$if(institute)$
\institute{$for(institute)$$institute$$sep$ \and $endfor$}
$endif$
$if(titlegraphic)$
\titlegraphic{\includegraphics{$titlegraphic$}}
$endif$
$if(logo)$
\logo{\includegraphics{$logo$}}
$endif$
$endif$

\begin{document}
$if(has-frontmatter)$
\frontmatter
$endif$
$if(title)$
$if(beamer)$
\frame{\titlepage}
$else$
\maketitle
$endif$

%%%%%%%%%% START AFTER TITLE PARTIAL %%%%%%%%%%%%%
$if(authblk)$
$for(author)$
$if(author.corresponding_author)$
\makeatletter\anotebycode{$author.name$@CORRESP}\makeatother
$endif$
$for(author.footnote)$
\anotebycode{$author.footnote$}
$endfor$
$endfor$
$endif$

$if(fancyhdr.first)$
\thispagestyle{myfirst}
$endif$

$if(fancyhdr.subsequent)$
\pagestyle{mysubsequent}
$endif$
%%%%%%%%%% END AFTER TITLE PARTIAL %%%%%%%%%%%%%

$if(abstract)$
\begin{abstract}
$abstract$
\end{abstract}
$endif$
$endif$

$for(include-before)$
$include-before$

$endfor$
$if(toc)$
$if(toc-title)$
\renewcommand*\contentsname{$toc-title$}
$endif$
$if(beamer)$
\begin{frame}[allowframebreaks]
$if(toc-title)$
  \frametitle{$toc-title$}
$endif$
  \tableofcontents[hideallsubsections]
\end{frame}
$else$
{
$if(colorlinks)$
\hypersetup{linkcolor=$if(toccolor)$$toccolor$$else$$endif$}
$endif$
\setcounter{tocdepth}{$toc-depth$}
\tableofcontents
}
$endif$
$endif$
$if(lof)$
\listoffigures
$endif$
$if(lot)$
\listoftables
$endif$
$if(linestretch)$
\setstretch{$linestretch$}
$endif$
$if(has-frontmatter)$
\mainmatter
$endif$
$body$

$if(has-frontmatter)$
\backmatter
$endif$
$if(natbib)$
$if(bibliography)$
$if(biblio-title)$
$if(has-chapters)$
\renewcommand\bibname{$biblio-title$}
$else$
\renewcommand\refname{$biblio-title$}
$endif$
$endif$
$if(beamer)$
\begin{frame}[allowframebreaks]{$biblio-title$}
  \bibliographytrue
$endif$
  \bibliography{$for(bibliography)$$bibliography$$sep$,$endfor$}
$if(beamer)$
\end{frame}
$endif$

$endif$
$endif$
$if(biblatex)$
$if(beamer)$
\begin{frame}[allowframebreaks]{$biblio-title$}
  \bibliographytrue
  \printbibliography[heading=none]
\end{frame}
$else$
\printbibliography$if(biblio-title)$[title=$biblio-title$]$endif$
$endif$

$endif$

$for(include-after)$
$include-after$

$endfor$
\end{document}
```
