---
title: Template for RFMO working papers
author:
  - name: Alice Anonymous
    email: alice@example.com
    corresponding_author: TRUE # Automatic author note including email address
    affiliation:
      - ABC
      - DEF
  - name: Bob Security
    email: bob@example.com
    affiliation: DEF
    footnote: 1 # Author note using reference
  - name: Cat Memes
    email: cat@anotheru.edu
    affiliation: Another University
    footnote:
        - 1
        - 2
address:
  - code: ABC
    address: University of Somewhere
  - code: DEF
    address: Address in one element deprecated, but works
  - code: Another University
    address: Address for Another University
footnote:
  - code: 1
    text: "Equal contribution"
  - code: 2
    text: "Current email address: [cat@example.com](mailto:cat@example.com)"
abstract:
  - text: |
      This is the first paragraph of the abstract. It has several sentences making it go over several lines. For this it needs to have a lot of text.
  
      This is the second paragraph.
  # - text: |
  #     Un resumen en español.
  #   babel-lang: spanish
  #   name: Resumen
  - text: |
      ::: {lang=fr}
      Voici un abstract en francais.
      :::
    name: Résumé
# Specifying lang=fr doesn't work for some reason, probably a bug in the texlive-lang-french package. 
# Using a span to specify abstract language generally works, but language doesn't get language into `otherlangs` variable. Need a span in the actual document text for this. Using an empty span at beginning of document for this purpose.
# Span with spanish doesn't seem to create spanish environment for some reason.
keywords:
  - keyword1
  - keyword2
  - keyword3
#classoptions:
#  - a4paper # Can also be here
bibliography: mybibfile.bib
csl: dmk-format.csl # Use any CSL style. Ignored if citation_package: natbib
link-citations: TRUE
output:
  pdf_document:
    keep_tex: TRUE
    template: template.tex
    md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: TRUE
numberlines: FALSE
authblk: FALSE # Set to false to put author affiliations in footnotes
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE
tables: TRUE
fancyhdr:
  first:
    headleft: "Report No. 1"
    headright: "Kaplan et al. (2021)"
    headrulewidth: 0pt
    #footleft: A left foot
    footrulewidth: 0pt
  subsequent:
    headright: "*Kaplan et al. (2021)*" # Italics
    headrulewidth: 1pt
    footrulewidth: 0pt
#header-includes:
#  - \usepackage[nomarkers,tablesfirst]{endfloat} # For figures and tables at end
#  - \usepackage{lineno}\linenumbers # For line numbering
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) # By default, hide code; set to TRUE to see code
knitr::opts_chunk$set(fig.pos = 'th') # Places figures at top or here
knitr::opts_chunk$set(out.width = '100%', dpi=300) # Figure resolution and size
knitr::opts_chunk$set(fig.env="figure") # Latex figure environment

options(knitr.table.format="latex") # For kable tables to work without setting format option
```

<!--
::: {lang=es}
:::
-->

::: {lang=fr}
:::

<!--
::: {lang=pt}
:::
-->

# Introduction

This template is a generic paper template that can be used for lots of tasks, including creating working group papers and as a starter format for publications for which one has not yet decided on a final format.

## A subsection

A numbered list:

1) First point
2) Second point
    - Subpoint
    
A bullet list:

* First point
* Second point

# Literature citations

By default, citations are handled using CSQL style files, but `natbib` citations are also possible.

Here are two sample references: 

* **author (year) example:** @horvath2018dna showed some really cool things. Only seems to work properly if `namedate: TRUE`. 
* **(author year) example:** This is a well known result [@ji20123d]. 

The bibliography will appear at the end of the document.

# Equations

An equation without a label for cross-referencing:

$$
E=mc^2
$$

An inline equation: $y=ax+b$

An equation with a label for cross-referencing:

\begin{equation}\label{eq:eq1}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = 1
\end{equation}

This equation can be referenced as follows: Eq. \ref{eq:eq1}

# Inserting R figures

The code below creates a figure. The code is included in the output because `echo=TRUE`.

```{r fig1, fig.cap="This is the first figure.",echo=TRUE}
plot(1:10,main="Some data",xlab="Distance (cm)",
     ylab="Time (hours)")
```

You can reference this figure as follows: Fig. \ref{fig:fig1}.

# Tables

## Generate a table using `xtable`

```{r xtabletable, results="asis", echo=TRUE}
df = data.frame(ID=1:3,code=letters[1:3])

# Creates tables that follow OUP guidelines 
# using xtable
library(xtable) 
print(xtable(df,caption="This is a xtable table.",
             label="tab:tab1"),
      comment=FALSE,caption.placement="top")
```

You can reference this table as follows: Table \ref{tab:tab1}.

## Generate a table using `kable`

```{r kabletable, echo=TRUE}
df = data.frame(ID=1:3,code=letters[1:3])

# kable can alse be used for creating tables
knitr::kable(df,caption="This is a kable table.",
             #format="latex",
             booktabs=TRUE,label="tab2")
```

You can reference this table as follows: Table \ref{tab:tab2}.


# Cross-referencing sections

You can cross-reference sections and subsections as follows: Section \ref{literature-citations} and Section \ref{a-subsection}.

For more portable and flexible referencing of sections, equations, figures and tables, use [`bookdown::pdf_document2`](https://github.com/rstudio/bookdown).

***Note:*** the last section in the document will be used as the section title for the bibliography.

<!-- An unnumbered section with the acknowledgements-->
# Acknowledgements {-}

This is an acknowledgement.

It consists of two paragraphs.

# References
